### 2022-08-20 manuscript.Rmd
Add colorbar, caption to TFR plots
Figures 2, 3, 4

@@

```{r, fig2, fig.height=10, include=TRUE, eval=FALSE}
# Read grand-averaged power
tfr_grand_ave <- read_csv(here(output_dir, "tfr_grand_ave.csv"))

# Create topographic plots for event-related power in each phase
tfr_plots <- plot_fig2(tfr_grand_ave, tfr_clusters, channel_locations)

@@

```{r, fig2b, fig.height=10, include=TRUE}
# Plot Insight Phase
tfr_plots[[2]]
```

```{r, fig2c, fig.height=10, include=TRUE}
# Plot Post-Insight Phase
tfr_plots[[3]]
```

>>>>

# Read grand-averaged power
tfr_grand_ave <- read_csv(here(output_dir, "tfr_grand_ave.csv"))

@@

```{r, fig2, fig.height=11, fig.cap="(ref:figure-2-caption)", include=TRUE}
# Create topographic plots for event-related power in each phase
tfr_plots <- plot_fig2(tfr_grand_ave, tfr_clusters, channel_locations)

@@

(ref:figure-2-caption) Time-frequency results for the pre-insight phase.
Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the naive condition, grand-averaged across participants.
A cluster-based permutation test indicated no clusters for which this difference was statistically significant (all $p$s > `r print_p(min(filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Naive")$p_val))`).

```{r, fig3, fig.height=11, fig.cap="(ref:figure-3-caption)", include=TRUE}
# Plot Insight Phase
tfr_plots[[2]]
```

(ref:figure-3-caption) Time-frequency results for the insight phase.
Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the naive condition, grand-averaged across participants.
Black dots highlight EEG channels that were part of a cluster for which this difference was statistically significant ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Naive" & p_val < 0.05)$p_val))`).

```{r, fig4, fig.height=11, fig.cap="(ref:figure-4-caption)", include=TRUE}
# Plot Post-Insight Phase
tfr_plots[[3]]
```

(ref:figure-4-caption) Time-frequency results for the post-insight phase.
Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the naive condition, grand-averaged across participants.
Black dots highlight EEG channels that were part of a cluster for which this difference was statistically significant ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Naive" & p_val < 0.05)$p_val))`).
